---
title: "MEDS Snapshot: `r params$condition`"
output: html_document
params:
  condition: "holder"
  selected_meds: "holder"
  acr50_val: "holder"
  das28_val: "holder"
  haq_val: "holder"
  disc_val: "holder"
  si_val: "holder"
  ijr_val: "holder"
  ra_data: "holder"
---

<style>
  .flat-table {
    display: block;
    font-family: sans-serif;
    -webkit-font-smoothing: antialiased;
    font-size: 115%;
    overflow: auto;
    width: auto;
  }
  h1 {
  color: #145369;
  font-weight: bold;
  }
  table {
  width: 100%;
  margin-bottom: 0px !important;
  }
  thead {
    background-color: #0079C2;
    color: white;
    font-weight: normal;
    padding: 20px 30px;
    text-align: center;
  }
  tbody {
    background-color: rgb(255, 255, 255);
    color: rgb(111, 111, 111);
    padding: 20px 30px;
  }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "asis")

library(kableExtra)
library(knitr)
library(dplyr)
library(openxlsx)
library(ggplot2)
library(ggrepel)
library(reactable)
library(reactablefmtr)
library(tippy)

acr50.val <- params$acr50_val
das28.val <- params$das28_val
haq.val <- params$haq_val
disc.val <- params$disc_val
si.val <- params$si_val
ijr.val <- params$ijr_val
meds.selected <- params$selected_meds
ra_data <- params$ra_data
```

<img style="float: right; width: 200px; margin-top: -50px" src="https://www.bcbs.com/themes/custom/bcbs/img/full-logo.svg">

Most recent literature search: November 30, 2018 

\

```{r}
# drugs <- meds.selected
# d1 <- data.frame(drugs) %>% rename('Drug Set' = 'drugs')
# d1 <- kbl(d1) %>%
#   kable_styling(bootstrap_options = "striped", full_width = T, position = "left")
# d1
ncol.split <- round(length(meds.selected)/2, digits = 0) + 1
col1 <- data.frame(x = meds.selected[1:ncol.split])
col2 <- data.frame(x2 = meds.selected[(ncol.split+1):length(meds.selected)])

for (i in 1:(nrow(col1) - nrow(col2))) {
  col2[nrow(col2)+1,] <- NA
}

data <- cbind(col1, col2)

data <- sapply(data, as.character) 
data[is.na(data)] <- ""
d1 <- kbl(data, col.names = NULL) %>%
  kable_styling(bootstrap_options = "striped", full_width = T, position = "left") %>%
  add_header_above(c("Drug Set" = 2))
d1
```

```{r}

### Efficacy measures
acr50 <- paste0("ACR 50 (", acr50.val, "% weight)")
das28 <- paste0("DAS 28 (", das28.val, "% weight)")
haq <- paste0("HAQ 50 (", haq.val, "% weight)")
data <- c(acr50, das28, haq)
d1 <- data.frame(data) %>% rename('Efficacy Measures' = 'data')

### Safety measures
disc <- paste0("Discontinuation (", disc.val, "% weight)")
si <- paste0("Serious Infection (", si.val, "% weight)")
ijr <- paste0("Injection Site Reaction (", ijr.val, "% weight)")
data <- c(disc, si, ijr)
d2 <- data.frame(data) %>% rename('Safety Measures' = 'data')

data <- cbind(d1, d2)

d1 <- kbl(data) %>%
  kable_styling(bootstrap_options = "striped", full_width = T, position = "left")
d1
```

\

```{r}

data <- ra_data[,c("Arm", "cNNT","cNNH","ceRank","AVScore")]

rt <- reactable(
  data,
  filterable = TRUE, 
  outlined = TRUE,
  showPageSizeOptions = TRUE,
  defaultColDef = colDef(
    align = "center",
    vAlign = "center"
  ),
  columns = list(
    Arm = colDef(header = with_tooltip("Medication", "Medications for the disease/condition included in the analysis.")),
    cNNT = colDef(header = with_tooltip("Composite NNT", "Composite Numbers Needed to Treat: Weighted average of numbers needed to treat to achieve benefits outcomes.")),
    cNNH = colDef(header = with_tooltip("Composite NNH", "Composite Numbers Needed to Harm: Weighted average of numbers needed to treat to achieve harms outcomes.")),
    ceRank = colDef(header = with_tooltip("Clinical Effectiveness Ranking", "Clinical Effectiveness Ranking based on each drug's distance of composite NNT/NNH from the median composite NNT/NNH. Click on 'More Info' for the calculation methodology and examples."),
                    align = "center",
                    vAlign = "center",
                    style = function(value) {
                      if (value == "F") { 
                        background <- "#ff8086" 
                        color = "#47292b"
                      }
                      else if (value == "D") { 
                        background <- "#faf29d" 
                        color = "#73705a"
                      }
                      else if (value == "C") { 
                        background <- "#e6e6e6" 
                        color = "#4a4a4a"
                      }
                      else if (value == "B") { 
                        background <- "#71bceb" 
                        color = "#344957"
                      }
                      else if (value == "A") { 
                        background <- "#c8f5b3" 
                        color = "#2b3d23"
                      }
                      else { 
                        background <- "#FF4E4E" 
                        color = "#47292b"
                      }
                      list(background = background, color = color)
                    }),
    
    AVScore = colDef(header = with_tooltip("Adjusted Value Score", "Adjusted value score is the estimated percentage of full value after discounting the difference in benefitted vs not benefitted ratio calculated using optimum NNT and observed NNT for the drug. Adjusted value score above 100 is assigned as 100 and adjusted value score below 0 is assigned 0."))
  )
)

rt

```

\

```{r}

default_data <- readRDS("ra_data_default.RDS")
default_data <- default_data[,c("Arm", "cNNT","cNNH","ceRank","AVScore")]

rt1<-reactable(
  default_data,
  filterable = TRUE, 
  outlined = TRUE,
  showPageSizeOptions = TRUE,
  defaultColDef = colDef(
    align = "center",
    vAlign = "center"
  ),
  columns = list(
    Arm = colDef(header = "Medication"),
        cNNT = colDef(header = "Composite NNT"),
        cNNH = colDef(header = "Composite NNH"),
        ceRank = colDef(header = "Clinical Effectiveness Ranking"),
    # Arm = colDef(header = with_tooltip("Medication", "Medications for the disease/condition included in the analysis.")),
    # cNNT = colDef(header = with_tooltip("Composite NNT", "Composite Numbers Needed to Treat: Weighted average of numbers needed to treat to achieve benefits outcomes.")),
    # cNNH = colDef(header = with_tooltip("Composite NNH", "Composite Numbers Needed to Harm: Weighted average of numbers needed to treat to achieve harms outcomes.")),
    # ceRank = colDef(header = with_tooltip("Clinical Effectiveness Ranking", "Clinical Effectiveness Ranking based on each drug's distance of composite NNT/NNH from the median composite NNT/NNH. Click on 'More Info' for the calculation methodology and examples."),
                    align = "center",
                    vAlign = "center",
                    style = function(value) {
                      if (value == "F") { 
                        background <- "#ff8086" 
                        color = "#47292b"
                      }
                      else if (value == "D") { 
                        background <- "#faf29d" 
                        color = "#73705a"
                      }
                      else if (value == "C") { 
                        background <- "#e6e6e6" 
                        color = "#4a4a4a"
                      }
                      else if (value == "B") { 
                        background <- "#71bceb" 
                        color = "#344957"
                      }
                      else if (value == "A") { 
                        background <- "#c8f5b3" 
                        color = "#2b3d23"
                      }
                      else { 
                        background <- "#FF4E4E" 
                        color = "#47292b"
                      }
                      list(background = background, color = color)
                    }),
    
    AVScore = colDef(header = with_tooltip("Adjusted Value Score", "Adjusted value score is the estimated percentage of full value after discounting the difference in benefitted vs not benefitted ratio calculated using optimum NNT and observed NNT for the drug. Adjusted value score above 100 is assigned as 100 and adjusted value score below 0 is assigned 0."))
  )
)

rt1

```


\

```{r, figures-side, fig.show="hold", out.width="50%"}

d1 <- kbl(data.frame(""), col.names = NULL) %>%
  kable_styling(bootstrap_options = NULL, full_width = T, position = "left") %>%
  add_header_above(c("Adjusted Value Score" = 1))
d1

data <- ra_data %>%
  mutate(MeanLL = as.numeric(MeanLL)) %>%
  mutate(MeanUL = as.numeric(MeanUL))

data.A <- data %>% filter(ceRank == 'A')
data.B <- data %>% filter(ceRank == 'B')

# 'A' Ranking
g1 <- ggplot(data.A, aes(x=MeanLL, xend=MeanUL, y=Arm, yend=Arm, color=ceRank)) +
  theme_bw() + 
  geom_segment(size = 8, color = "#A3E982") + 
  labs(title=NULL, x=NULL, y=NULL) +
  scale_x_continuous(n.breaks = 10) +
  theme(legend.position="none",
        panel.border = element_blank(),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 12)
        ) 

# 'B' Ranking 
g2 <- ggplot(data.B, aes(x=MeanLL, xend=MeanUL, y=Arm, yend=Arm, color=ceRank)) +
  theme_bw() + 
  geom_segment(size = 8, color = "#0074BB") + 
  labs(title=NULL, x=NULL, y=NULL) +
  scale_x_continuous(n.breaks = 10) +
  theme(legend.position="none",
        panel.border = element_blank(),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 12)
        ) 

par(mar = c(4, 4, .1, .1))
plot(g1)
plot(g2)

```

\
\

```{r}

div(h5(paste0("Snapshot created on: ", format(Sys.time(), "%I:%M %p %Z  %m-%d-%Y"))), 
    style = "font-family: sans-serif; 
    color: #145369;
    font-weight: bold;")

```