---
title: "MEDS Snapshot: `r params$condition`"
output: html_document
params:
  condition: "holder"
  selected_meds: "holder"
  bc_val: "holder"
  ho_data: "holder"
---

<style>
  .flat-table {
    display: block;
    font-family: sans-serif;
    -webkit-font-smoothing: antialiased;
    font-size: 115%;
    overflow: auto;
    width: auto;
  }
  h1 {
  color: #145369;
  font-weight: bold;
  }
  table {
  width: 100%;
  margin-bottom: 0px !important;
  }
  thead {
    background-color: #0079C2;
    color: white;
    font-weight: normal;
    padding: 20px 30px;
    text-align: center;
  }
  tbody {
    background-color: rgb(255, 255, 255);
    color: rgb(111, 111, 111);
    padding: 20px 30px;
  }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "asis")

library(kableExtra)
library(knitr)
library(dplyr)
library(openxlsx)
library(ggplot2)
library(ggrepel)

bc.val <- params$bc_val
meds.selected <- params$selected_meds
ho_data <- params$ho_data
```

<img style="float: right; width: 200px; margin-top: -50px" src="https://www.bcbs.com/themes/custom/bcbs/img/full-logo.svg">


Most recent literature search: January 8, 2020

\

```{r}
### Population
x <- paste0("Adults (18 years or older) with severe Hemophilia A (Factor VIII Levels <1% or <2%)")
data <- data.frame(x) %>% rename('Population' = 'x')

d1 <- kbl(data, align = "c") %>%
  kable_styling(bootstrap_options = "striped", full_width = T, position = "left")
d1
```

```{r}
ncol.split <- round(length(meds.selected)/2, digits = 0) + 1
col1 <- data.frame(x = meds.selected[1:ncol.split])
col2 <- data.frame(x2 = meds.selected[(ncol.split+1):length(meds.selected)])

for (i in 1:(nrow(col1) - nrow(col2))) {
  col2[nrow(col2)+1,] <- NA
}

data <- cbind(col1, col2)

data <- sapply(data, as.character) 
data[is.na(data)] <- ""
d1 <- kbl(data, col.names = NULL, align = c("c", "c")) %>%
  kable_styling(bootstrap_options = "striped", full_width = T, position = "left") %>%
  add_header_above(c("Drug Set" = 2))
d1
```

```{r}

### Efficacy measures
bc <- paste0("Bleeding control using 1-2 infusion (", bc.val, "% weight)")
data <- data.frame(bc) %>% rename('Efficacy Measures' = 'bc')

d1 <- kbl(data, align = "c") %>%
  kable_styling(bootstrap_options = "striped", full_width = T, position = "left")
d1

### Safety measures
x <- paste0("None (The incidence of the develoment of inhibitors was too small to detect a difference, with most studies reporting zero)")
data <- data.frame(x) %>% rename('Safety Measures' = 'x')

d1 <- kbl(data, align = "c") %>%
  kable_styling(bootstrap_options = "striped", full_width = T, position = "left")
d1
```

\

```{r, fig.width = 12, fig.align = 'center', echo = FALSE, warning = FALSE}

d1 <- kbl(data.frame(""), col.names = NULL) %>%
  kable_styling(bootstrap_options = NULL, full_width = T, position = "left") %>%
  add_header_above(c("Clinical Effectiveness" = 1))
d1

data <- ho_data %>%
  select('Name', 'ceRank', 'LL', 'UL')

data$Name <- factor(data$Name, levels = data$Name)
data$ceRank <- factor(data$ceRank, levels = c("A", "B", "C", "D", "F"))

data2 <- data %>% filter(ceRank %in% c('A', 'B'))

center.line <- min(data2$LL)

data.up <- data %>%
  filter(LL >= center.line) %>%
  mutate('end' = center.line) %>%
  mutate('start' = UL) %>%
  arrange(desc(start))

data.down <- data %>%
  filter(LL < center.line) %>%
  mutate('end' = LL) %>%
  mutate('start' = center.line) %>%
  arrange(desc(end))

data <- rbind(data.up, data.down)
data$id <- seq_along(data$Name)

data <- data %>% 
  rename("Ranking" = 'ceRank',
         "Drug" = 'Name')

p <- ggplot(data, aes(`Drug`, fill = `Ranking`)) + 
  geom_rect(aes(x = `Drug`,
                xmin =`id` -0.5, 
                xmax = `id` +0.5, 
                ymin = `end`,
                ymax = `start`)) +
  scale_fill_manual(values = c("A" = "#A3E982",
                               "B" = "#0074BB",
                               "C" = "#E3E3E3",
                               "D" = "#FDF59F",
                               "F" = "#FF4E4E")) +
  scale_x_discrete(labels = ~data$Drug) +
  scale_y_continuous(n.breaks = 10) +
  theme_bw()  +
  theme(legend.position = c(0.05, 0.3),
        legend.background = element_rect(fill="transparent"),
        panel.border = element_blank(),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 12)
  )
plot(p)

```

\

```{r, figures-side, fig.show="hold", out.width="50%"}

d1 <- kbl(data.frame(""), col.names = NULL) %>%
  kable_styling(bootstrap_options = NULL, full_width = T, position = "left") %>%
  add_header_above(c("Adjusted Value Score" = 1))
d1

data <- ho_data %>%
  mutate(MeanLL = as.numeric(LL)) %>%
  mutate(MeanUL = as.numeric(UL)) 

data.A <- data %>% filter(ceRank == 'A')
data.B <- data %>% filter(ceRank == 'B')

# 'A' Ranking
g1 <- ggplot(data.A, aes(x=MeanLL, xend=MeanUL, y=Name, yend=Name, color=ceRank)) +
  theme_bw() +
  geom_segment(size = 8, color = "#A3E982") +
  labs(title=NULL, x=NULL, y=NULL) +
  scale_x_continuous(n.breaks = 10) +
  theme(legend.position="none",
        panel.border = element_blank(),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 12)
        )

# 'B' Ranking
g2 <- ggplot(data.B, aes(x=MeanLL, xend=MeanUL, y=Name, yend=Name, color=ceRank)) +
  theme_bw() +
  geom_segment(size = 8, color = "#0074BB") +
  labs(title=NULL, x=NULL, y=NULL) +
  scale_x_continuous(n.breaks = 10) +
  theme(legend.position="none",
        panel.border = element_blank(),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 12)
        )

par(mar = c(4, 4, .1, .1))
plot(g1)
plot(g2)

```

\
\


```{r}

div(h5(paste0("Snapshot created on: ", format(Sys.time(), "%I:%M %p %Z  %m-%d-%Y"))), 
    style = "font-family: sans-serif; 
    color: #145369;
    font-weight: bold;")

```
