---
title: "MEDS Snapshot: `r params$condition`"
output: html_document
params:
  condition: "holder"
  selected_meds: "holder"
  disprog_val: "holder"
  rf_val: "holder"
  disc_val: "holder"
  hepatox_flu_val: "holder"
  ijr_dr_val: "holder"
  ms_data: "holder"
---

<style>
  .flat-table {
    display: block;
    font-family: sans-serif;
    -webkit-font-smoothing: antialiased;
    font-size: 115%;
    overflow: auto;
    width: auto;
  }
  h1 {
  color: #145369;
  font-weight: bold;
  }
  table {
  width: 100%;
  margin-bottom: 0px !important;
  }
  thead {
    background-color: #0079C2;
    color: white;
    font-weight: normal;
    padding: 20px 30px;
    text-align: center;
  }
  tbody {
    background-color: rgb(255, 255, 255);
    color: rgb(111, 111, 111);
    padding: 20px 30px;
  }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "asis")

library(kableExtra)
library(knitr)
library(dplyr)
library(openxlsx)
library(ggplot2)
library(ggrepel)

disprog.val <- params$disprog_val
rf.val <- params$rf_val
disc.val <- params$disc_val
hepatox_flu.val <- params$hepatox_flu_val
ijr_dr.val <- params$ijr_dr_val
meds.selected <- params$selected_meds
ms_data <- params$ms_data
```

<img style="float: right; width: 200px; margin-top: -50px" src="https://www.bcbs.com/themes/custom/bcbs/img/full-logo.svg">


Most recent literature search: January 7, 2021

\

```{r}
### Population
x <- paste0("Adults (18 years or older) with relapsing remitting or progressive multiple sclerosis")
data <- data.frame(x) %>% rename('Population' = 'x')

d1 <- kbl(data, align = "c") %>%
  kable_styling(bootstrap_options = "striped", full_width = T, position = "left")
d1
```


```{r}
ncol.split <- round(length(meds.selected)/2, digits = 0) + 1
col1 <- data.frame(x = meds.selected[1:ncol.split])
col2 <- data.frame(x2 = meds.selected[(ncol.split+1):length(meds.selected)])

for (i in 1:(nrow(col1) - nrow(col2))) {
  col2[nrow(col2)+1,] <- NA
}

data <- cbind(col1, col2)

data <- sapply(data, as.character) 
data[is.na(data)] <- ""
d1 <- kbl(data, col.names = NULL) %>%
  kable_styling(bootstrap_options = "striped", full_width = T, position = "left") %>%
  add_header_above(c("Drug Set" = 2))
d1
```

```{r}

### Efficacy measures
disprog <- paste0("EDSS (", disprog.val, "% weight)")
rf <- paste0("% Who are replapse-free (", rf.val, "% weight)")
empty <- paste0(" ")
data <- c(disprog, rf, empty)
d1 <- data.frame(data) %>% rename('Efficacy Measures' = 'data')

### Safety measures
disc <- paste0("Discontinuation (", disc.val, "% weight)")
hepatox_flu <- paste0("Liver toxicity / Flu-like reactions (", hepatox_flu.val, "% weight)")
ijr_dr <- paste0("Injection Site Reaction / Diarrhea (", ijr_dr.val, "% weight)")
data <- c(disc, hepatox_flu, ijr_dr)
d2 <- data.frame(data) %>% rename('Safety Measures' = 'data')

data <- cbind(d1, d2)

d1 <- kbl(data) %>%
  kable_styling(bootstrap_options = "striped", full_width = T, position = "left")
d1
```

\

```{r, fig.align = 'center'}

d1 <- kbl(data.frame(""), col.names = NULL) %>%
  kable_styling(bootstrap_options = NULL, full_width = T, position = "left") %>%
  add_header_above(c("Clinical Effectiveness" = 1))
d1

medsMS <- ms_data %>%
  rename("Composite.NNH" = "cNNH",
         "Composite.NNT" = "cNNT",
         "Clinical.effectiveness.ranking" = "ceRank",
         "Adjusted.Value.Score" = "AVScore",
         "Name" = "Arm")

medsMS$cRDBen<-1/medsMS$Composite.NNT
medsMS<-medsMS %>%
  mutate(pc_rank_ben = rank(cRDBen)/length(cRDBen))
medsMS$fromNNT<-(medsMS$pc_rank_ben-0.5)*100
medsMS$cRDHarm<-1/medsMS$Composite.NNH
medsMS<-medsMS %>%
  mutate(pc_rank_harm = rank(cRDHarm)/length(cRDHarm))
medsMS$fromNNH<-(0.5-medsMS$pc_rank_harm)*100
medsMS$Name2<-sub("\\+.*", "", medsMS$Name)
medsMS$Composite.NNH1<-ifelse(medsMS$Composite.NNH<=500,medsMS$Composite.NNH,ifelse(medsMS$Composite.NNH<11000,NA,medsMS$Composite.NNH-10500))
medsMS <- medsMS[!is.na(medsMS$Composite.NNH1) ,]
names(medsMS)[names(medsMS) == "Clinical.effectiveness.ranking"] <- "Ranking"

g<-ggplot(medsMS[which(medsMS$Ranking=="A"|medsMS$Ranking=="B"),], aes(y=fromNNT, x=fromNNH))+
  geom_point(aes(col=Name2,shape=Ranking), size=3)+ 
  geom_label_repel(aes(label=Name2),show.legend = FALSE, size=3, hjust = 0.5, vjust = 0.5, fill = alpha(c("white"),0.5))+
  theme(
    legend.position="bottom",
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 2),
    axis.title=element_text(size=15)
  )+
  scale_color_discrete(guide='none')+
  scale_x_continuous("% point from median composite NNH", breaks=c(-50,-20,0,20,50), limits = c(-50,50))+
  scale_y_continuous("% point from median composite NNT", breaks=c(-50,-20,0,20,50))
plot(g)

```

\

```{r, figures-side, fig.show="hold", out.width="50%"}

d1 <- kbl(data.frame(""), col.names = NULL) %>%
  kable_styling(bootstrap_options = NULL, full_width = T, position = "left") %>%
  add_header_above(c("Adjusted Value Score" = 1))
d1

data <- ms_data %>%
  mutate(MeanLL = as.numeric(MeanLL)) %>%
  mutate(MeanUL = as.numeric(MeanUL))

data.A <- data %>% filter(ceRank == 'A')
data.B <- data %>% filter(ceRank == 'B')

# 'A' Ranking
g1 <- ggplot(data.A, aes(x=MeanLL, xend=MeanUL, y=Arm, yend=Arm, color=ceRank)) +
  theme_bw() + 
  geom_segment(size = 8, color = "#A3E982") + 
  labs(title=NULL, x=NULL, y=NULL) +
  scale_x_continuous(n.breaks = 10) +
  theme(legend.position="none",
        panel.border = element_blank(),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 12)
        ) 

# 'B' Ranking 
g2 <- ggplot(data.B, aes(x=MeanLL, xend=MeanUL, y=Arm, yend=Arm, color=ceRank)) +
  theme_bw() + 
  geom_segment(size = 8, color = "#0074BB") + 
  labs(title=NULL, x=NULL, y=NULL) +
  scale_x_continuous(n.breaks = 10) +
  theme(legend.position="none",
        panel.border = element_blank(),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 12)
        ) 

par(mar = c(4, 4, .1, .1))
plot(g1)
plot(g2)

```

\
\

```{r}

div(h5(paste0("Snapshot created on: ", format(Sys.time(), "%I:%M %p %Z  %m-%d-%Y"))), 
    style = "font-family: sans-serif; 
    color: #145369;
    font-weight: bold;")

```

