---
title: "test" 
output: html_document
---
<style>
  .flat-table {
    display: block;
    font-family: sans-serif;
    -webkit-font-smoothing: antialiased;
    font-size: 115%;
    overflow: auto;
    width: auto;
  }
  h1 {
  color: #145369;
  font-weight: bold;
  }
  table {
  width: 100%;
  margin-bottom: 0px !important;
  }
  thead {
    background-color: #0079C2;
    color: white;
    font-weight: normal;
    padding: 20px 30px;
    text-align: center;
  }
  tbody {
    background-color: rgb(255, 255, 255);
    color: rgb(111, 111, 111);
    padding: 20px 30px;
  }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "asis")

library(kableExtra)
library(knitr)
library(dplyr)
library(openxlsx)
library(ggplot2)
library(ggrepel)
library(shiny)

# condition <- params$condition
# meds.selected <- params$selected_meds
# EOS_val <- params$EOS_val
# VR_val <- params$VR_val
# Dis_SA_val <- params$Dis_SA_val
# Ad_Ef_val <- params$Ad_Ef_val
# sa_data <- params$sa_data
data <- readRDS("SA_Data")
condition <- "CONDITION"
meds.selected <- data$Arm
EOS_val <- 30
VR_val <- 70
Dis_SA_val <- 70
Ad_Ef_val <- 30
sa_data <- data
```


<img style="float: right; width: 200px; margin-top: -50px" src="https://www.bcbs.com/themes/custom/bcbs/img/full-logo.svg">


Most recent literature search: January 1, 2020

\

```{r}
### Population
x <- paste0("Individuals ages 12 years and older with moderate to severe allergic asthma or eosinophilic asthma")
data <- data.frame(x) %>% rename('Population' = 'x')

d1 <- kbl(data, align = "c") %>%
  kable_styling(bootstrap_options = "striped", full_width = T, position = "left")
d1
```

```{r}
ncol.split <- round(length(meds.selected)/2, digits = 0) + 1
col1 <- data.frame(x = meds.selected[1:ncol.split])
col2 <- data.frame(x2 = meds.selected[(ncol.split+1):length(meds.selected)])

for (i in 1:(nrow(col1) - nrow(col2))) {
  col2[nrow(col2)+1,] <- NA
}

data <- cbind(col1, col2)

data <- sapply(data, as.character)
data[is.na(data)] <- ""
d1 <- kbl(data, col.names = NULL, align = c("c", "c")) %>%
  kable_styling(bootstrap_options = "striped", full_width = T, position = "left") %>%
  add_header_above(c("Drug Set" = 2))
d1
```

```{r}

### Efficacy measures
eos <- paste0("Acute exacerbation of asthma (", EOS_val, "% weight)")
vr <- paste0("Rate of hospitalization/ED visit (", VR_val, "% weight)")

data <- c(eos, vr)
d1 <- data.frame(data) %>% rename('Efficacy Measures' = 'data')

### Safety measures
disc <- paste0("Discontinuation (", Dis_SA_val, "% weight)")
sae <- paste0("Serious adverse events (", Ad_Ef_val, "% weight)")
data <- c(disc, sae)
d2 <- data.frame(data) %>% rename('Safety Measures' = 'data')

data <- cbind(d1, d2)

d1 <- kbl(data) %>%
  kable_styling(bootstrap_options = "striped", full_width = T, position = "left")
d1

```

\


```{r, fig.width = 12, fig.align = 'center', echo = FALSE, warning = FALSE}

# d1 <- kbl(data.frame(""), col.names = NULL) %>%
#   kable_styling(bootstrap_options = NULL, full_width = T, position = "left") %>%
#   add_header_above(c("Clinical Effectiveness" = 1))
# d1
# 
# data <- ho_data %>%
#   select('Name', 'ceRank', 'LL', 'UL')
# 
# data$Name <- factor(data$Name, levels = data$Name)
# data$ceRank <- factor(data$ceRank, levels = c("A", "B", "C", "D", "F"))
# 
# data2 <- data %>% filter(ceRank %in% c('A', 'B'))
# 
# center.line <- min(data2$LL)
# 
# data.up <- data %>%
#   filter(LL >= center.line) %>%
#   mutate('end' = center.line) %>%
#   mutate('start' = UL) %>%
#   arrange(desc(start))
# 
# data.down <- data %>%
#   filter(LL < center.line) %>%
#   mutate('end' = LL) %>%
#   mutate('start' = center.line) %>%
#   arrange(desc(end))
# 
# data <- rbind(data.up, data.down)
# data$id <- seq_along(data$Name)
# 
# data <- data %>% 
#   rename("Ranking" = 'ceRank',
#          "Drug" = 'Name')
# 
# p <- ggplot(data, aes(`Drug`, fill = `Ranking`)) + 
#   geom_rect(aes(x = `Drug`,
#                 xmin =`id` -0.5, 
#                 xmax = `id` +0.5, 
#                 ymin = `end`,
#                 ymax = `start`)) +
#   scale_fill_manual(values = c("A" = "#A3E982",
#                                "B" = "#0074BB",
#                                "C" = "#E3E3E3",
#                                "D" = "#FDF59F",
#                                "F" = "#FF4E4E")) +
#   scale_x_discrete(labels = ~data$Drug) +
#   scale_y_continuous(n.breaks = 10) +
#   theme_bw()  +
#   theme(legend.position = c(0.05, 0.3),
#         legend.background = element_rect(fill="transparent"),
#         panel.border = element_blank(),
#         axis.text.y = element_text(size = 12),
#         axis.text.x = element_text(size = 12)
#   )
# plot(p)

```

\

```{r, figures-side, fig.show="hold", out.width="50%"}
# 
# d1 <- kbl(data.frame(""), col.names = NULL) %>%
#   kable_styling(bootstrap_options = NULL, full_width = T, position = "left") %>%
#   add_header_above(c("Adjusted Value Score" = 1))
# d1
# 
# data <- ho_data %>%
#   mutate(MeanLL = as.numeric(LL)) %>%
#   mutate(MeanUL = as.numeric(UL)) 
# 
# data.A <- data %>% filter(ceRank == 'A')
# data.B <- data %>% filter(ceRank == 'B')
# 
# # 'A' Ranking
# g1 <- ggplot(data.A, aes(x=MeanLL, xend=MeanUL, y=Name, yend=Name, color=ceRank)) +
#   theme_bw() +
#   geom_segment(size = 8, color = "#A3E982") +
#   labs(title=NULL, x=NULL, y=NULL) +
#   scale_x_continuous(n.breaks = 10) +
#   theme(legend.position="none",
#         panel.border = element_blank(),
#         axis.text.y = element_text(size = 12),
#         axis.text.x = element_text(size = 12)
#         )
# 
# # 'B' Ranking
# g2 <- ggplot(data.B, aes(x=MeanLL, xend=MeanUL, y=Name, yend=Name, color=ceRank)) +
#   theme_bw() +
#   geom_segment(size = 8, color = "#0074BB") +
#   labs(title=NULL, x=NULL, y=NULL) +
#   scale_x_continuous(n.breaks = 10) +
#   theme(legend.position="none",
#         panel.border = element_blank(),
#         axis.text.y = element_text(size = 12),
#         axis.text.x = element_text(size = 12)
#         )
# 
# par(mar = c(4, 4, .1, .1))
# plot(g1)
# plot(g2)

```